---
output:
  word_document: default
  html_document: default
---
#Econ 211- Assignment 1

Ans 1. 
  i) 
    C~3~^5^ = 5! / 3! (5 - 3)! = 5 * 4 / 2 = 10
    Therefore the total number of samples in the sample space are 10
    samples will be the following:
        {1,2,3} or {40, 80, 80} 
        {1,2,4} or {40, 80, 60}
        {1,2,5} or {40, 80, 20}
        {1,3,4} or {40, 80, 60}
        {1,3,5} or {40, 80, 20}
        {1,4,5} or {40, 60, 20}
        {2,3,4} or {80, 80, 60}
        {2,3,5} or {80, 80, 20}
        {2,4,5} or {80, 60, 20}
        {3,4,5} or {80, 60, 20}
        
ii)
    mean = x~1~+x~2~+x~3~ ... x~n~ / n
    the sample mean of each set is as follows:
    {40, 80, 80} = 66.66
    {40, 80, 60} = 60
    {40, 80, 20} = 46.66
    {40, 80, 60} = 60
    {40, 80, 20} = 46.66
    {40, 60, 20} = 40
    {80, 80, 60} = 73.33
    {80, 80, 20} = 60
    {80, 60, 20} = 53.33
    {80, 60, 20} = 53.33
    
iii)
    P(A) = # of outcomes in S consistent with A/ # of outcomes in S
    P(X = 50) = 0 / 10 = 0 or 0%
    P(X > 50) = 7 / 10 or 70%
    
Ans 2.
  i)
```{r}
ec221_assn1 <- read.csv("ec221_assn1.csv")
summary(ec221_assn1)
table(ec221_assn1)
```
  We can see from the above exercise that the population size is 50 an the distribution of values is: 5 values of 20, 25 of 40, and 20 of 60.
 ii)
```{r}
x <- ec221_assn1[,1]
x <- as.numeric((unlist(x)))
hist(x)
```
    8 bins are used in the histogram, I think the number of bins is appropriate as: there are not too less a bins(here there are only three values as the variable x and all are in separate bins); also there are not too many bins as we have depicted the spread in the values, and the lack of values in between. 
    The addition of any more bins will add unecessary white space and make the histogram less readable.
    The subtraction of bins will make the variance and the distribution of values less clear. The histogram then will neglect the lack of values between the given three values.
  iii)
```{r}
choose(50,3)
```
Therefore 19600 distinct samples can be formed.
  iv) 
    The only values the sample mean can take our 
    {20, 
    40,
    60, 
    33.33, 
    26.66, 
    46.66, 
    53.33}
    
v) The total number of cases here is: C~3~^50^ = 19600(we got this in part iii).
The cases where the sample is {60, 60, 60} will have a sample mean over 50. And these will be:
C~3~^20^
```{r}
choose(20,3)
```
therefore C~3~^20^= 
The cases where the sample is {60, 60, 40} will have a sample mean over 50. And these will be:
(C~2~^20^)*(C~1~^25^)
```{r}
choose(20,2)
choose(25,1)
```
therefore (C~2~^20^)*(C~1~^25^) =